Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-25 VMCAI-revised-version/final.tex
up

In the case of $\pred$-basis-effective upward compatible WSTS, {\sc Resilience} is undecidable when $\Safe = \mathop{\downarrow} \Safe$.

@@

\begin{proof}
\nocite{araki1976PN,dufourd1998reset}
{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some state $q_f$ is equivalent to
deciding structural termination of reset-VASS, which is undecidable.
\qed \end{proof}
\mathieu{GOTO}

>>>>

In the case of $\pred$-basis-effective upward compatible WSTS, {\sc Resilience} is undecidable when $\Safe = \mathop{\downarrow} \Safe$.  This stems from the fact
{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some control-state $q_f$ is equivalent to
deciding structural termination of reset-VASS, which is undecidable.

Indeed, the structural termination problem consists in deciding if %the termination problem holds for 
a system terminates on every initial state. 
Since termination is w.l.o.g. reachability of $q_f({\bf 0})$ \mathieu{est-ce qu'on a pas besoin d'une hypothèse d'être deterministic ici pour que ce soit vraiment w.l.o.g. ??} for some control state $q_f$, we can formulate the structural termination problem as

\problemx{Structural termination}
{A reset-VASS $V=(Q,T)$ of dimension $d$, a control state $q_f \in Q$.}
{ $Q \times \N^d \longrightarrow^{*} q_f({\bf 0})$ ? \\}

The undecidability of which leads to the following proposition.

\mathieu{GOTO}

@@

\nocite{araki1976PN,dufourd1998reset}
\iffalse
\begin{proof}
{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some state $q_f$ is equivalent to
deciding structural termination of reset-VASS, which is undecidable.
\qed \end{proof}
\fi
